Backward designing a reproducible framework for undergraduate data science research

### 2019-12-04 Rmd/methods.Rmd
upd

We designed and used a framework for mentored undergraduate data science research 
projects with big data. Below, we describe our initial implementation of the framework before relating 
it to three major ideas from @nolan2010computing.

>>>>

We used backward design principles to create and implement a 
framework for mentored undergraduate data science research 
projects with big data. Below, we describe our use of 
backward design and ideas from @nolan2010computing.
We then detail our framework and its initial implementation.

## Framework design

We started with the backward design principles from @wiggins2005understanding. We prioritized
